### 2017-02-03 local-capability-machine.tex
Indentation
changes/corrections to f1 proof

                  (\reg_0\update{\pcreg}{c_\malloc}\update{r_0}{c_{f1}''}\update{r_1}{\dots}\update{r_l}{c_l},m'')

@@

                \item $\cdots$ represents the needed size for the activation record. 

@@

                \item $\dom(\hs_{\var{ar}}) = [b,e]$

@@

                \item $c_{\var{ar}}' = ((\entry,\local)b,e,b+\olf)$ where $b+\olf$ is the first address of the activation code.

@@

                  [2 \mapsto \iota_{f1}]
                  [3 \mapsto \iota_{\var{ar}}]
                  [4 \mapsto \iota_l]
                  [5 \mapsto \iota_\flag]
                  [5 \mapsto \iota_\link]$
                \lau{Need to change this to use the new standard regions}
                \item $\iota_{f1}$, $\iota_{\var{ar}}$, $\iota_l$, $\iota_\flag$, and $\iota_\link$ are permanent islands that only accepts respectively $\ms_{f1}$, $\ms_{\var{ar}}$, $\ms_l$, $\ms_\flag$, and $\ms_\link$.

@@

                  \item Show: $\iota^{\nwl,p}_{\start_\adv,\addrend_\adv} \nsubsim[n] \iota^\pwl_{\start_\adv,\addrend_\adv}$: $\iota^{\nwl,p}_{\start_\adv,\addrend_\adv}
                    \nsubsim[n] \iota^\pwl_{\start_\adv,\addrend_\adv}$: see Lemma~\ref{lem:nwlp-subset-pwl}.

@@

                Let $n' = n - j - j'$ and show

@@

                \item $n' \leq n$
                  \item trivial

@@

                      \item Show $\forall a \in [\start_\adv,\addrend_\adv] \ldotp \npair[n'-1]{\ms(a)} \in \stdvr(W)$
                      (non-local requirement trivial - only capability if the link one, and it is $\glob$).
                      \item $a \neq \start_\adv$ : trivial, contains instruction only.

@@

                        SFTS $\iota_{\link} \nsubsim[n'] \iota^\pwl_{\link,\link+1}$\\
                        $\iota_{\link}$ accepts only $\ms_\link$, so show:
                        \item $\npair[n'-1]{c_\malloc} \in \stdvr(W)$: We assume
                          this is indeed the case.\dominique{TODO: prove}
                        \item $\npair[n'-1]{c_\adv} \in \stdvr(W)$: for $n'' <
                          n'-1$ and $W' \futurestr W$ show:
                          \\$\npair[n'']{\updatePcPerm{c_\adv}} \in \stdvr(W')$.
                          Use FTLR.\dominique{no: by induction hypothesis?} \label{f1:adv}
                    \item The remaining islands are designed to accept their designated islands.
                \item $\npair[n']{\reg_0\update{\pcreg}{\updatePcPerm{c_{\var{adv}}}}\update{r_1}{c_{\var{adv}}}\update{r_0}{c_{ar}'}} \in \stdrr(W)$
                  \item case: $\npair[n']{c_{\var{adv}}} \in \stdvr(W)$
                    \item Similar to \ref{f1:adv}
                  \item case: $\npair[n']{c_{\var{ar}}'} \in \stdvr(W)$.
                    \item Let $n'' < n'$ and $W' \futurewk W$ be given and show $\npair[n'']{\updatePcPerm{c_{\var{ar}}'}} \in \stdvr(W')$\\
                      Let $n^{(3)} \leq n''$, $\heapSat[\ms']{n''}{W'}$, and $\npair[n^{(3)}]{\reg}$ be given\\
                      Show: $\npair[n^{(3)}]{(\reg\update{\pcreg}{\updatePcPerm{c_{\var{ar}}'}},\ms')} \in \observations(W')$\\
                      Assume $(\reg\update{\pcreg}{\updatePcPerm{c_{\var{ar}}'}},\ms' \uplus \ms_{\var{frame}}) \step[k''] (\halted, m')$, for some $k''$, $m'$ and $\ms_{\var{frame}}$. Due to $\heapSat[\ms']{n''}{W'}$, $\ms_{f1}$, $\ms_\flag$, $\ms_{\var{ar}}'$, and $\ms_l$ are unchanged. \\
                      The execution loads $c_l$ to $r_l$ and jumps to $c_{f1}^{(3)}$ (the point just before the assertion). As $\ms_l = 1$, the assertion is successful and the execution halts. In other words, there were no changes to the memory.\\
                      Use $W'$, $\ms_r = \emptyset$, and $\ms'$ to get the desired result, i.e., $m' = \ms' \uplus \ms_{\var{frame}}$ and $\heapSat[\ms']{n''-k''}{W'}$ (using downwards closure of memory satisfaction).          
                  \item case: $\npair[n']{0} \in \stdvr(W)$
                    \item Trivial
                Get
                  \npair[n']{(\reg_0\update{\pcreg}{\updatePcPerm{c_{\var{adv}}}}\update{r_1}{c_{\var{adv}}}\update{r_0}{c_{ar}'},\ms)} \in \observations(W)
                By initial assumption of the lemma, the execution halts. Use $\ms_{\var{frame}}$, $m'$ and the number of steps it takes to halt to get:
                $W' \futurestr W$, $\ms_r$ and $\ms'$ s.t. $m' = \ms_r \uplus \ms' \uplus \ms_{\var{frame}}$ and $\heapSat[\ms']{n' - \dots}{W'}$. As $\iota_\flag$ is a permanent region, we know it is still in $W'$, so $m'(\flag) = 0$.

@@

To show
\[
  \npair[n-i]{(\reg',\ms' \uplus [\start_\stk \mapsto 1] \uplus \ms_\stk |_{\start_\stk+1,\addrend_\stk})} \in \observations(W)
\]
We use Lemma~\ref{lem:scall-works} which requires us to show
\begin{enumproof}
  \item $\memSat[n-i]{\ms'}{W}$ \\
    Partition $\ms'$ as follows:
    \begin{enumproof}
      \item $\ms_\malloc$: governed by $\iota_{\malloc,0}$, use malloc specification.
      \item $\ms_\flag \uplus \ms_{f2}$: governed by island 1, only this memory segment is accepted.
      \item $\ms_\link$: governed by island 2, only this memory segment is accepted.
      \item $\ms_\adv$:\\
        show
        \[
          \npair[n]{\ms_\adv} \in H^\pwl_{\start_\adv,\addrend_\adv}\;1\;\xi^{-1}(W)
        \]
        this is trivial except for showing
        \[
          \npair[n-1]{c_\link} \in \stdvr(W)
        \]
        amounts to showing
        \[
          \npair[n-1]{\link,\link+1} \in \readCond{}(\glob)(W)
        \]
        which follows from
        \begin{enumproof}
          \item $\npair[n-1]{c_\adv} \in \stdvr(W)$: \label{item:f3:adv1}\\
            We will show
            \begin{equation}
              \label{eq:f3:adv-in-stder}
              \forall W' \futurestr W \ldotp \npair{c_\adv} \in \stdvr(W')
            \end{equation}
            which will give us \ref{item:f3:adv1} using downwards closure.

>>>>

    (\reg_0\update{\pcreg}{c_\malloc}\update{r_0}{c_{f1}''}\update{r_1}{\var{len}_{\var{ar}}}\update{r_l}{c_l},m'')

@@

  \item $\var{len}_{\var{ar}}$ is the needed size for the activation record. 

@@

  \item $\dom(\hs_{\var{ar}}) = [b,e]$, and $e-b = \var{len}_{\var{ar}}$

@@

  \item $c_{\var{ar}}' = ((\entry,\local)b,e,b+\var{offset})$ where $b+\var{offset}$ is the first address of the activation code.

@@

    [2 \mapsto \iota^\sta (\perm,\ms_{f1} \uplus \ms_{\var{ar}} \uplus \ms_l \uplus \ms_\flag)]
    [3 \mapsto \iota^{\sta,u}(\perm,\ms_\link)]$

@@

    \item Show: $\iota^{\nwl,p}_{\start_\adv,\addrend_\adv} \nsubsim[n] \iota^\pwl_{\start_\adv,\addrend_\adv}$: Follows from Lemma~\ref{lem:nwlp-subset-pwl}.

@@

  Let $n' = n - j - j'-k-k'$ and show

@@

@@

        \item Show $\forall a \in [\start_\adv,\addrend_\adv] \ldotp (\npair[n'-1]{\ms(a)} \in \stdvr(W) \land \nonlocal{\ms(a)})$
        \item $a \neq \start_\adv$ : trivial, contains instruction only and they are non-local.

@@

          $\glob$ capabilities are non-local.\\
          SFTS $\iota^{\sta,u}(\perm,\ms_\link) \nsubsim[n'] \iota^\pwl_{\link,\link+1}$ which follows from Lemma~\ref{lem:stau-subset-pwl}.
        \item $\npair[n']{\ms_\link} \in H^{\sta,u}(1)(W)$:\\
          This boils down to showing:
          \item $\npair[n'-1]{c_\malloc} \in \stdvr(W)$: Follows from Lemma~\ref{lem:malloc-in-vr}.

          \item $\npair[n'-1]{c_\adv} \in \stdvr(W)$: for $n'' <
            n'-1$ and $W' \futurestr W$ show:
            \\$\npair[n'']{\updatePcPerm{c_\adv}} \in \stder(W')$.
            Use FTLR. \label{f1:adv}
          \end{enumproof}
        \end{enumproof}
      \item The last case follows from Lemma~\ref{lem:mem-sat-static}
      \end{enumproof}
    \end{enumproof}
  \item $\npair[n']{\reg_0\update{\pcreg}{\updatePcPerm{c_{\var{adv}}}}\update{r_1}{c_{\var{adv}}}\update{r_0}{c_{ar}'}} \in \stdrr(W)$
    \begin{enumproof}
    \item case: $\npair[n']{c_{\var{adv}}} \in \stdvr(W)$
      \begin{enumproof}
      \item Similar to \ref{f1:adv}
      \end{enumproof}
    \item case: $\npair[n']{c_{\var{ar}}'} \in \stdvr(W)$.
      \begin{enumproof}
      \item Let $n'' < n'$ and $W' \futurewk W$ be given and show $\npair[n'']{\updatePcPerm{c_{\var{ar}}'}} \in \stder(W')$\\
        Let $n^{(3)} \leq n''$, $\heapSat[\ms']{n^{(3)}}{W'}$, and $\npair[n^{(3)}]{\reg}$ be given\\
        Show: $\npair[n^{(3)}]{(\reg\update{\pcreg}{\updatePcPerm{c_{\var{ar}}'}},\ms')} \in \observations(W')$\\
        Assume $(\reg\update{\pcreg}{\updatePcPerm{c_{\var{ar}}'}},\ms' \uplus \ms_{\var{frame}}) \step[k''] (\halted, m')$, for some $k'' \leq n^{(3)}$, $m'$ and $\ms_{\var{frame}}$. Due to $\heapSat[\ms']{n^{(3)}}{W'}$, $\ms_{f1}$, $\ms_\flag$, $\ms_{\var{ar}}'$, and $\ms_l$ are unchanged. \\
        The execution loads $c_l$ to $r_l$ and jumps to $c_{f1}^{(3)}$ (the point just before the assertion). As $\ms_l = 1$, the assertion is successful and the execution halts. In other words, there were no changes to the memory.\\
        Use $W'$, $\ms_r = \emptyset$, and $\ms'$ to get the desired result, i.e., $m' = \ms' \uplus \ms_{\var{frame}}$ and $\heapSat[\ms']{n^{(3)}-k''}{W'}$ (using downwards closure of memory satisfaction).          
      \end{enumproof}
    \item case: $\npair[n']{0} \in \stdvr(W)$ (the contents remaining registers)\\
      Trivial to show.
    \end{enumproof}
  \end{enumproof}
  Get
  \[
    \npair[n']{(\reg_0\update{\pcreg}{\updatePcPerm{c_{\var{adv}}}}\update{r_1}{c_{\var{adv}}}\update{r_0}{c_{ar}'},m^{(3)})} \in \observations(W)
  \]
  By initial assumption of the lemma, the execution halts. Use $\ms_{\var{frame}}$, $m'$ and the number of steps it takes to halt to get:
  $W' \futurestr W$, $\ms_r$ and $\ms'$ s.t. $m' = \ms_r \uplus \ms' \uplus \ms_{\var{frame}}$ and $\heapSat[\ms']{n}{W'}$. As $\iota_\flag$ is a permanent region, we know it is still in $W'$, so $m'(\flag) = 0$.
\end{proof}

@@

To show
\[
  \npair[n-i]{(\reg',\ms' \uplus [\start_\stk \mapsto 1] \uplus \ms_\stk |_{\start_\stk+1,\addrend_\stk})} \in \observations(W)
\]
We use Lemma~\ref{lem:scall-works} which requires us to show
\begin{enumproof}
  \item $\memSat[n-i]{\ms'}{W}$ \\
    Partition $\ms'$ as follows:
    \begin{enumproof}
      \item $\ms_\malloc$: governed by $\iota_{\malloc,0}$, use malloc specification.
      \item $\ms_\flag \uplus \ms_{f2}$: governed by region 1, only this memory segment is accepted.
      \item $\ms_\link$: governed by region 2, only this memory segment is accepted.
      \item $\ms_\adv$:\\
        show
        \[
          \npair[n]{\ms_\adv} \in H^\pwl_{\start_\adv,\addrend_\adv}\;1\;\xi^{-1}(W)
        \]
        this is trivial except for showing
        \[
          \npair[n-1]{c_\link} \in \stdvr(W)
        \]
        amounts to showing
        \[
          \npair[n-1]{\link,\link+1} \in \readCond{}(\glob)(W)
        \]
        which follows from
        \begin{enumproof}
          \item $\npair[n-1]{c_\adv} \in \stdvr(W)$: \label{item:f3:adv1}\\
            We will show
            \begin{equation}
              \label{eq:f3:adv-in-stder}
              \forall W' \futurestr W \ldotp \npair{c_\adv} \in \stdvr(W')
            \end{equation}
            which will give us \ref{item:f3:adv1} using downwards closure.
